SummaryStats

### 2023-03-02 analysis/code/Exploration.Rmd
clarify deaths, extinctions, treatments

```{r lineage level data}
terrs <- data %>% 
  distinct(terr_id, year, .keep_all=TRUE) %>% 
  select(terr_id, year, territory, count_cities, final_year, extinction)

@@

# create plot with no outliers
size_time_no_outliers <- terrs_centuries %>% 
  ggplot() + 
  geom_boxplot(aes(x = century, y = count_cities), outlier.shape = NA) +
  coord_cartesian(ylim = quantile(terrs_centuries$count_cities, c(0, 0.96)))

@@

size_ext_no_outliers <- terrs_life %>% 
  ggplot() + 
  geom_boxplot(aes(x = extinction_ever, y=max_size), outlier_shape = NA) +
  coord_cartesian(ylim = quantile(terrs_life$max_size, c(0, 0.9)))

>>>>

```{r lineage level data}
terrs <- data %>% 
  distinct(terr_id, year, .keep_all=TRUE) %>% 
  select(terr_id, year, territory, count_cities, final_full_year, extinction)

@@

# create plot with no outliers
size_time_no_outliers <- terrs_centuries %>% 
  ggplot() + 
  geom_boxplot(aes(x = century, y = count_cities), outlier.shape = NA) +
  coord_cartesian(ylim = quantile(terrs_centuries$count_cities, c(0, 0.93)))

@@

size_ext_no_outliers <- terrs_life %>% 
  ggplot() + 
  geom_boxplot(aes(x = extinction_ever, y=max_size), outlier.shape = NA) +
  coord_cartesian(ylim = quantile(terrs_life$max_size, c(0, 0.93)))
